MSDS6372Project2

### 2021-03-27 MSDS6372Project2.Rmd
minoro update

# summary(linear.model2) tells us there might be a perfect correlation between Not-Known between workclass and occupation
# Following code to verify if this is true
adult.temp = adult %>% filter(workclass=="Not-Known"|occupation=="Not-Known") %>% select(workclass,occupation)
#view(adult.temp)
# There is a perfect correlation existed between missingi values of workclass and occupation in original dataset
summary(workclass)
summary(occupation)

@@

```{r}
# It will be interesting to first perform a PCA and look at how numeric variables can contribute to predicting the response
reduced<-adult[,-c(2,4,6,7,8,9,10,14,15)]
# There are only five numeric variables including education.num which derived from education
pc.result<-prcomp(reduced,scale.=TRUE)
pc.scores<-pc.result$x

>>>>

######## This Code part has been readdressed at the above importing section #############################################
# summary(linear.model2) tells us there might be a perfect correlation between Not-Known between workclass and occupation
# Following code to verify if this is true
#adult.temp = adult %>% filter(workclass=="Not-Known"|occupation=="Not-Known") %>% select(workclass,occupation)
#view(adult.temp)
########################################################################################################################
# There is a perfect correlation existed between missingi values of workclass and occupation in original dataset
summary(workclass)
summary(occupation)

@@

```{r}
# It will be interesting to first perform a PCA and look at how numeric variables can contribute to predicting the response
reduced<-adult[,-c(2,4,6,7,8,9,10,14,15,16)]
# There are only five numeric variables including education.num which derived from education
pc.result<-prcomp(reduced,scale.=TRUE)
pc.scores<-pc.result$x
